AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-25 paper.tex
Add specs in appendices, mention of Arduino Bus Library
Add reference to NMEA code library
Proof read abstract done

\documentclass[11pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{titlesec}
\usepackage{float}
\usepackage{color}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{bytefield}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{csvsimple}
\usepackage{hyperref}

@@

\usepackage[detect-weight=true, binary-units=true]{siunitx}
\usepackage{tikz}
\usepackage[justification=centering,labelfont={small,bf},font={small,bf}]{caption}
\usepackage[scaled]{beramono} % BitStream Vera font (code)
\usepackage[T1]{fontenc}
\usepackage[a4paper, margin=3cm]{geometry}
\usepackage[nottoc]{tocbibind}
\usepackage{array}

@@

\begin{abstract}
\end{abstract}

\tableofcontents
\setlength{\parskip}{1em}

@@

>>>>

\documentclass[11pt]{report}
\usepackage[scaled]{beramono} % BitStream Vera font (code)
\usepackage[T1]{fontenc}
\usepackage[a4paper, margin=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{titlesec}
\usepackage{float}
\usepackage{color}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{bytefield}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{csvsimple}
\usepackage{hyperref}
\usepackage{booktabs}

@@

\usepackage[detect-weight=true, binary-units=true]{siunitx}
\usepackage{tikz}
\usepackage[justification=centering,labelfont={small,bf},font={small,bf}]{caption}
\usepackage[titletoc,toc,page]{appendix}
\usepackage[nottoc]{tocbibind}
\usepackage{array}
\usepackage{etoolbox}

% reinstate the correct level for list of tables and figures
\appto\listoffigures{\addtocontents{lof}{\protect\setcounter{tocdepth}{1}}}
\appto\listoftables{\addtocontents{lot}{\protect\setcounter{tocdepth}{1}}}

@@

\begin{abstract}

The aim of this project was to investigate the design options for a modular payload bus for \acrfull{hab} missions, and to evaluate one such design by implementing in in hardware and software.

High-Altitude Ballons (HAB) provide affordable access to near-space conditions, even for low-budget entities (universities, schools and amateurs). While current low-budget missions rely on commercial off-the-shelf computers and sensors, their architecture and software are often custom-made and targeted for a single use. This prevents easy reuse of hardware and software components, and raises the barrier to entry by requiring non-trivial networking and computing skills.

This paper presents the development of the \acrfull{ahabus}, solution designed by applying the modular bus model used by most modern satellites to \acrlong{hab} architectures. An \acrfull{obc} running a common flight software (\acrshort{fcore}) provides facilities for position tracking and reliable radio telemetry to a ground station, and polls data from payloads, custom for each flight.

The resulting protocols and platform prototype were successful and passed both day-in-the-life testing and radio channel resilience tests. Further testing of the \acrshort{ahabus} platorm and minor modifications to the Payload Bus and Radio Communications protocols will be required in order to qualify the platform for in-flight use. Once these steps are taken, \acrshort{ahabus} could render scientific \acrlong{hab} missions more accessible and affordable by allowing students and researchers to focus on payload design and development.

\end{abstract}

\tableofcontents

@@

\setlength{\parskip}{1em}
